Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increases Repair Time?

### 2015-03-04 phaseDelay.tex
Added correlation and bug distribution

>>>>

The distribution of defects found and fixed per phase is shown in Figure~\ref{fig:fix-phase-dist}. A high percentage of defects were found and fixed in the early phases, i.e., requirements, high level design, and design reviews and inspections.

\begin{figure*}[!t]
\begin{center}
\includegraphics{fix-phase-dist.png}
\end{center}
\caption{Distribution of defects found and fixed by phase.}
\label{fig:fix-phase-dist}
\end{figure*}

In the TSP data, there is a weak correlation (Kendall's $\tau = 0.19, p < 0.01, 95\% CI$) between a defect's cost-to-fix (minutes of effort) and the defects phase delay (phase removed - phase injected). The correlations were also calculated for each phase, e.g., does the phase delay of defects found in Test correlate with the defect's cost-to-fix (Table~\ref{tab:phase_corr}).

\begin{table}[ht]
\centering
\begin{tabular}{lll}
  Phase & $tau$ & $p$ \\ 
  \hline
BeforeDevelopment & NA & -- \\ 
  Planning & NA & -- \\ 
  Reqts & NA & -- \\ 
  ReqtsReview & 0.05 & 0.01 \\ 
  ReqtsInspect & 0.17 & $<$0.01 \\ 
  HLD & NA & -- \\ 
  HLDReview & 0.04 & 0.24 \\ 
  HLDInspect & -0.07 & 0.05 \\ 
  Design & 0.19 & 0.08 \\ 
  DesignReview & 0.08 & $<$0.01 \\ 
  DesignInspect & 0.06 & $<$0.01 \\ 
  Code & 0.21 & $<$0.01 \\ 
  CodeReview & 0.15 & $<$0.01 \\ 
  CodeInspect & 0.11 & $<$0.01 \\ 
  Test & 0.16 & $<$0.01 \\ 
  QualTest & NA & -- \\ 
  IntTest & 0.13 & $<$0.01 \\ 
  SysTest & 0.32 & $<$0.01 \\ 
  AcceptTest & 0.07 & 0.29 \\ 
  \end{tabular}
\caption{Correlation of cost-to-fix and phase delay for defects found in each phase (Kendall's $\tau$)} 
\label{tab:phase_corr}
\end{table}
